---
title: "Assignment_7"
format: html
editor: visual
---

```{r}
#| echo: false
#| warning: false
library(dplyr)
library(tidyr)
library(reactable)
library(ggplot2)
library(plotly)
library(crosstalk)
```

Problem 1:

```{r}
df <- data.frame(
x = c(5, 1, 4, NA, NA, NA, 2, 1),
y = c(5, NA, 3, 2, 5, NA, 2, 1),
z = c(1, 4, 2, 5, 2, NA, 5, 4),
t = c(4, 2, NA, 1, 5, 2, 3, 3)
)
corxy <- cor(df$x,df$y, use = "pairwise.complete.obs")
corzy <- cor(df$z,df$y, use = "pairwise.complete.obs")
corty <- cor(df$t,df$y, use = "pairwise.complete.obs")

y_pref <- 3 + (2 - 3.33)

y_pref


```

Problem 2:

```{r}
movie1 <- c(5, 5, 1, 4)
movie2 <- c(1, NA, 4, 2)
movie3 <- c(4, 3, 2, NA)
movie4 <- c(NA, 2, 5, 1)
movie5 <- c(NA,5,2,5)
movie6 <- c(NA, NA, NA, 2)
movie7 <- c(2, 2, 5, 3)
movie8 <- c(1, 1, 4, 3)

cor12 <- cor(movie1,movie2, use = "pairwise.complete.obs")
cor13 <- cor(movie1,movie3, use = "pairwise.complete.obs")
cor14 <- cor(movie1,movie4, use = "pairwise.complete.obs")
cor15 <- cor(movie1,movie5, use = "pairwise.complete.obs")
cor16 <- cor(movie1,movie6, use = "pairwise.complete.obs")
cor17 <- cor(movie1,movie7, use = "pairwise.complete.obs")
cor18 <- cor(movie1,movie8, use = "pairwise.complete.obs")

cor12
cor13
cor14
cor15
cor16
cor17
cor18

```

Movie 1 has the highest correlation with Movie 5, so they are the most similar.

Problem 3A.

```{r}
df <- read.csv("http://manctsui.github.io/datasets/countries.csv")

df$Agriculture <-
 ifelse(is.na(df$Agriculture),
 mean(df$Agriculture, na.rm = TRUE),
  df$Agriculture)

df$Industry <-
 ifelse(is.na(df$Industry),
 mean(df$Agriculture, na.rm = TRUE),
  df$Industry)


 

```

Problem 3B:

```{r}
df1 <- read.csv("http://manctsui.github.io/datasets/countries.csv")
m = 0
nrow(df1)
for(i in 1:227) {
  if(is.na(df1[i,18])) {
  m = m + 1
  } }
m 

n = 0
for(i in 1:227) {
  if(is.na(df1[i,19])) {
  n = n + 1
  } }
n 


```

There are 15 NA's from Agriculture and 16 NA's for Industrial

Problem 4:

We can find the line of best fit using cor, sd, and the mean to find the b0 and b1 in b0 + b1x. The equation for b1 = r \* sy / sx and b0 = mean(y) - mean(x) \* b1.

For this problem Temp is our Y and Chirps is our x.

```{r}
df <- data.frame(
temp = c(79, 74, 73, 76, 82, 72, 71, 79, 83, 70, 73, 75, 77),
chirps = c(44, 40, 38, 43, 48, 37, 34, 45, 51, 32, 35, 42, 43)
)
#I will now find the sds, means, and corr.
cor <- cor(df$temp,df$chirps, use = "pairwise.complete.obs")
cor

sdtemp <- sd(df$temp) 
sdchirps <- sd(df$chirps)
mtemp <- mean(df$temp)
mchirps <- mean(df$chirps)

b1 = cor * (sdtemp / sdchirps)
b0 = mtemp - b1*mchirps
b1
b0

```

We can see that b1 = 0.714 and b0 = 46.47. This means that the intercept is 46.47 and the slope is 0.714. This is the same slope and intercept that the line of best fit gave us.
